Describing demographic models is hard

### 2020-05-19 paper.tex
added comment on MArtin et al

@@

\begin{figure}[ht]
\begin{center}
\makebox[\textwidth][c]{\includegraphics{figures/ooa_expected_stats.pdf}}
\caption{\textbf{Expected diversity statistics under the \citet{gutenkunst2009inferring} model}.
    \textbf{(A)} The correctly implemented model.
    \textbf{(B)} The incorrectly implemented model from the \msprime\ tutorial, with migration continuing
    into the past.
    \textbf{(C)} Marginal allele frequency spectra under the two models. Heterozygosity in the incorrect model
    is inflated by $~3.5\%$, though the general shape of the distributions are qualitatively similar.
    \textbf{(D)} Similarly, the increased heterozygosity leads to excess $D^2$, though the LD-decay is
    qualitatively similar between models.
    \textbf{(E-G)} True size history for each population plotted against the expected size history from
    the expected inverse coalescence rates.
    \sgcomment{Not sure what the 1 in Figure 1b means. I would put the mass migration arrow in blue. }
}
\label{fig:ooa_stats}
\end{center}
\end{figure}

>>>>

Finally, from a genetics perspective, the corrected simulations indicate that the accuracy of genetic risk scores
is still substantially reduced in understudied populations, supporting the main conclusion of~\citep{martin2017human}. 
However, the reduction is much less pronounced than reported. In particular, we did not observe large
differences in mean risk prediction across populations, as presented in~\citep{martin2017human} \sgcomment{check}.
Thus genetic drift alone does not appear to induce large biases in mean predicted risk across ethnicities, at least for 
the polygenic architectures considered here. \sgcomment{This might need some analytical backup}

@@
